How fluid-mechanical erosion creates anisotropic porous media

### 2022-06-29 docs/PhysicsPaper/StokesErosion.tex
NM

The previous section shows many intriguing features to arise as a randomly initialized configuration of solid bodies erodes. These observations natural raise the question: are the trends specific to the particular initializing chosen or do are they general features that emerge robustly? To answer this question, we now analyze the same quantities---permeability, tortuosity, and anisotropy---over an ensemble of many simulations having different numbers of bodies and different random initializations. We analyze runs having $M$ = 20, 40, 60, 80, and 100 bodies, with at least three different instances of each. This data set represents roughly 2,100 hours of computational time.

>>>>

The previous section shows intriguing features to arise from the erosion of a random initialization of solid bodies. The observations natural raise the question: are the trends specific to the particular simulation shown or do these features emerge robustly across different simulations? To answer this question, we now analyze the same quantities---permeability, tortuosity, and anisotropy---over an ensemble of many simulations having different numbers of bodies and different random initializations. We analyze runs having $M$ = 20, 40, 60, 80, and 100 bodies, with at least three different instances of each. This data set represents roughly 2,100 hours of computational time.
